Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

Now, we compute $\cross_H(r^*)$ for each $r^* \in R^*_i$ --- where $\cross_H(r^*)$, defined in \eqref{eqn:cross}, is the set of segments in $H$ crossing $r^*$ --- which is an instance of the find-all-sorted version of Problem $\mathscr{D}$.

@@

\section{Finding Result Tuples of Type 2} \label{sec:hv:type2}

>>>>

Now, we compute $\cross_H(r^*)$ for each $r^* \in R^*_i$ --- where $\cross_H(r^*)$, defined in \eqref{eqn:cross}, is the set of segments in $H$ crossing $r^*$ --- which is an instance of the find-all-sorted version of Problem $\mathscr{D}$. The following lemma, proven in Appendix~\ref{app:hv}, presents some crucial properties for these ``cross'' sets.

\begin{lemma} \label{lmm:hv:type1:cross-r*}
    Both statements below are true: 
    \myenums{
        \item $\sum_{i=1}^k \sum_{r^* \in R^*_i} |\cross_H(r^*)| \le \out$.

        \item Consider any $k$-tuple $\bm{t} \in \J(R'_1, ..., R'_{k-2})$. Let $r' = \gbot(\bm{t})$ and $r^*$ be the top-sliced rectangle of $r'$. Then, it must hold that $\dcross_H(\bm{t}) \subseteq \cross_H(r^*)$. Furthermore, if the segments of $\cross_H(r^*)$ have been sorted in ascending order, then $\dcross_H(\bm{t})$ includes a prefix of the sorted order.
    }
\end{lemma}

@@

\section{H-V $k$-SJ: Result Tuples of Type 2} \label{sec:hv:type2}
